% ******************************* Thesis Declaration ***************************

\begin{declaration}

This thesis represents original work by the author except for where specific reference is made to the work of others.
The presented work have not been submitted in whole or in part for consideration for any other degree or qualification in this, or any other university. 
Due to the collaborative nature of the modern particle experiments, the thesis here relies upon work performed by collaborators from the Short-Baseline Near Detector (SBND) as well as from other experiments.

The overviews of Heavy Neutral Leptons (HNLs) and physics of liquid argon time projection chambers, given in Chapters \ref{ChapterHNL} and \ref{Chapter3}, contain work which the author did not contribute.
References assign credit for the work and figures presented.

The overview of SBND given in Chapter \ref{ChapterDetector} relies on work performed by the entire SBND collaboration.
Plots, diagrams and photographs not made by the author are labelled with references to the original source.
In the scope of detector installation, the author helped with the cabling of the Photon Detection System (PDS) boxes and their installation to the detector alongside with B. Carlson and B. Bogart.
Moreover, the author performed the installation of the PDS readout electronics, under the guidance of M. Stancari and W. Badgett.

Also in Chapter \ref{ChapterDetector}, the flux prediction relies upon the Booster Neutrino Beam simulation developed in MiniBooNE \cite{BNBFlux}.
The flux simulation was performed by Z. Pavlovic and the flux reader was developed by M. Del Tutto. 
The neutrino fluxes of SBND were recently updated with a new kaon reweighting scheme from SciBooNE, which the author assisted with the flux validation \cite{SciBooNE}. 

In the simulation framework of SBND described in Chapter \ref{ChapterSim}, the author contributed in the development of the MeVPrtl generator for simulating beyond standard model particles.
This generator was a joint effort of SBND and ICARUS collaborators, lead by G. Putnam.
The author developed and validated physics of HNL simulation with R. Alvarez-Garrote and L. Pelegrina-Gutierrez.
The implementation of the generator into SBND was performed together with R. Alvarez-Garrote.
Moreover, the author identified and helped implementing a fix in the GENIE generator to enable the timing simulation of neutrino interactions, which was the key ingredient in the HNL analysis in this thesis.

In Chapter \ref{ChapterReco}, the reconstruction toolkit for the charge reconstruction, Wirecell and Pandora, were developed in MicroBooNE and ProtoDUNE prior to the author involvement.
The author updated the track-shower separation boosted decision tree within the Pandora framework, under the help of E. Tyley and D. Brailsford.
The PDS and CRT reconstruction and other high-level analysis tools were contributed by SBND collaborators with credits provided in the references.
Most importantly, the author would like to thank F. Nicolas-Arnaldos, R. Alvarez-Garrote, D. Garcia-Gamez and J. I. Crespo-Anadon, who pioneer the nanosecond timing reconstruction using the PDS, which the HNL analysis relies on.

The study timing study of the DAQ performance provided in Chapter \ref{ChapterDAQ}, relies on work performed by many SBND collaborators.
The hardware and software of the White Rabbit timing system as well as the CRT Sharps was setup before the author involvement.
The author contributed in the calibration and installation of the SPEC-TDC module and timing signal cabling under the guidance of G. A. Lukhanin and W. Badgett.
The timing characterisation of FEB modules was performed with the help of M. Stancari and H. Lay.
The timing characterisation of CAEN digitisers also received many inputs from M. Stancari.  

In Chapter \ref{ChapterCalib}, the presented work in the scope of charge calibration was performed under the guidance of M. Mooney and many discussions with G. Putnam and J. Mueller.
A summary of results from the ICARUS collaboration is included, with references assign credit in the work and figures presented.

The selection of HNLs presented in Chapter \ref{ChapterSelect} contains many elements in the selection are shared across SBND.
MC samples used in the selection was a collaborative work with H. Lay and R. Alvarez-Garrote.
The selection software framework was also constructed with a lot of help from H. Lay. 
Moreover, the cosmic rejection tools CRUMBS was developed by H. Lay, the flash matching OpT0 was developed by L. Tung and the particle identification tools Razzled was developed by H. Lay with groundwork done by E. Tyley.
Finally, the selection sparked many useful discussions and inputs from R. Alvarez-Garrote, L. Pelegrina-Gutierrez and J. I. Crespo-Anadon.

The uncertainty reweighting in Chapter \ref{ChapterResult} was performed using the framework shared across the SBND and ICARUS collaboration, developed before the author involvement.
The author would like to thank H. Lay, J. Mueller, and J. Kim for their help in understanding statistical, flux and cross section systematic uncertainties.
The procedure to set upper limits on the mixing of HNLs was performed using the PYHF package \cite{pyhf}, with advice from T. Junk to interpret the results.
Finally, the author would like to thank A. M. Szelc, whose original idea was to search for HNLs by exploiting their lateness, that started off this entire thesis.  

% Author and date will be inserted automatically from thesis.tex \author \degreedate

\end{declaration}

