% ************************** Thesis Acknowledgements **************************

\begin{acknowledgements}     
First and foremost, I would like to thank my mom and dad for supporting me emotionally and financially through my PhD.
I appreciate their trust in me to follow my passion in a foreign country away from home.
Without them, I would not be where I am today.

I would like to thank my supervisors Neil for accepting me into the physics program at Sheffield and Vitaly for taking the lead in the supervisor role.
I am grateful for the autonomy and freedom to explore my physics interests.
I understand that my PhD journey was a wild card with unfamiliar research topics and multiple last minute trips to Fermilab. 
Yet, they remained as accommodating and guiding as ever to keep me on the right track.

October 2020, at the peak of Covid, was certainly an odd time to move to a new city.
Somehow, the Sheffield group made it feel like home.                                  
Anthony and Ala, thank you for teaching me about actual hardware.
Ed, thank you for teaching me every possible thing that a first year PhD student should know.
Rhiannon and Anna, despite your later arrival, your support and positivity only add to my experience at Sheffield.

Ali, you were my very first friend in Sheffield and another fellow sharing the same PhD boat as me.   
As promised, I truly appreciate our Wednesday KFC after lab teaching, late night fried chicken orders and many more chicken-related memories that keep me afloat through difficult times.
                                                                                                                            
Working at SBND has only been an amazing experience that reassures my decision to pursue physics.
I owe thanks to so many people across various working groups for their support towards the completion of this thesis, and many more thanks to everyone in SBND for giving into my ideas during my term as SBND young representative.
Most importantly, I would like to give a special thanks to Michelle for her guidance not only at Fermilab but also on my journey at SBND.

\texttt{the-real-sbnd}, your friendships cannot go unmentioned.
Especially, Henry, this thesis would not exist without your help on every front.
Jiaoyang, thank you for joining the production team with me.
Rodrigo, thank you for cross checking my analysis in every step.
Fran, thank you for answering all my dumb PDS-related questions.
Lynn, thank you for all the plants and cat photos.
Bear, thank you for gaining me access to Zuko and Roo.
Mun, thank you for my very first Chicago tour.
Thank you all for the jokes and rants as we were doing our best to navigate through our PhD journeys.

Finally, Lane, words cannot describe your unconditional support through this entire experience.
Thank you for everything!                                                                                                                                       
\end{acknowledgements}
